A Survey on Ordered Binary Decision Diagrams

### 2015-09-13 paper.tex
Revise Compose operation (ITE operator)

\noindent
For a given node $x$, the ITE operator $ITE(x, hi(x), lo(x))$ chooses $hi(x)$ if
$x$ evaluates to true and $lo(x)$ otherwise. Computing $ITE(x, hi(x), lo(x))$ is
accomplished by utilizing the following recursive form:
\begin{center}
$
ITE(x, hi(x), lo(x)) =
(x, ITE(), ITE())
$
\end{center}

>>>>

\noindent
For a given node $x$, the ITE operator for three nodes, \newline
$ITE(x, hi(x), lo(x))$, chooses $hi(x)$ if $x$ evaluates to true and $lo(x)$
otherwise. Computing $ITE(x, hi(x), lo(x))$ is accomplished by utilizing a
recursive formulation~\cite{BRACE90}. To shorten the recursive formula, $l$ and
$h$ are used to represent $lo(x)$ and $hi(x)$, respectively.
\begin{center}
$
ITE(x, h, l) =
(var(x), ITE(x|_{x=1}, h|_{x=1}, l|_{x=1}), ITE(x|_{x=0}, h|_{x=0}, l|_{x=0}))
$
\end{center}

This formulation is based upon the fact, that every node $n$ of an OBDD represents
a Boolean function and is denoted by a triple $(var(n), hi(n), lo(n))$. Brace et
al.~\cite{BRACE90} called the variable associated with $n$, i.e. $x_n$ the
\textit{top variable} of $n$.
